eyeIntegration Viewing Stats

### 2019-06-04 src/viewing_stats.Rmd
massive update with text improvemetns, fixing sup tables (including order). updated viewing stats. added new sup figs for swaroop amd data.

Regular Map
```{r, fig.width = 6, fig.height=2}
ggplot(data = geo_locate, aes(x = longitudes, y = latitudes, colour = countries)) + 
  geom_map(data=world, map=world,
           aes(x=long, y=lat, map_id=region),
           color="#090D2A", fill="lightgray", size=0.05, alpha=1/4) + 
  geom_point() + 
  theme_void() +
  scale_color_viridis_d()

>>>>

Regular Map
```{r, fig.width = 6, fig.height=2}
world <- map_data("world")
world <- world[world$region != "Antarctica",]
ggplot(data = geo_locate, aes(x = longitudes, y = latitudes, colour = countries)) + 
  geom_map(data=world, map=world,
           aes(x=long, y=lat, map_id=region),
           color="#090D2A", fill="lightgray", size=0.05, alpha=1/4) + 
  geom_point() + 
  theme_void() +
  scale_color_viridis_d()
